Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\section{Building Brick Geometry Algorithms} \label{app:bricks}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{A}}$}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{B}}$}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{D}}$}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$}

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:cross-non-empty}.}

\extraspacing {\bf Correctness of Algorithm Generate-$S$.}

\section{Correctness of Algorithm generate-S} \label{app:hv:type1:gen-S}

\section{An $\bm{\Omega(n \log n)}$ Lower Bound for 2-SJ} \label{app:lb}

>>>>

\section{Building Brick Algorithms} \label{app:bricks}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{A}}$.}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{B}}$.}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$.}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{D}}$.}

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$.}

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:properties}.}
